The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
add all heatmap
Updates from ShareLaTeX

@@

>>>>

Table \ref{table:Recall} and figure \ref{fig:EclipseHeatmap} show the results of the EX3. In table \ref{table:Recall}, we presented the recall of each algorithms. The recall is the ratio between the number of $1$s in the decision vector $\textbf{x}$ and the number of resolved requirements in the real dataset. In ECLIPSE, FIREFOX-I, and FIREFOX-III, we can verify that each algorithms has a high recall values above 0.75 and the recall value increases as higher maximum profit was got in EX1. It can be easily confirmed on figure \ref{fig:EclipseHeatmap}. Therefore, we can concludet that the profit strategy of ECLIPSE, FIREFOX-I and FIREFOX-III are similar to the real world dataset.

However, in FIREFOX-II, all algorithms had lower recall values than other datasets. But we can see that AHP has much higher recall values than other algorithms.

In the table, we can verify that it has a high recall value as higher maximum profit in EX1, except FIREFOX-II.

@@

\begin{table*}[t]
\caption{EX3 - Recall of each algorithms on four datasets}
\begin{tabular}{@{}crrrrr@{}}
\toprule
\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6} 
\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{AHP} \\ \midrule
ECLIPSE & 0.77300 & 0.81435 & 0.82025 & \textbf{0.82700} & 0.82363\\
FIREFOX-I & 0.82973 & 0.00000 & 0.85876 & 0.86721 & \textbf{0.87302}\\
FIREFOX-II & 0.56917 & 0.00000 & 0.60507 & 0.61536 & \textbf{0.79725}\\
FIREFOX-III & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\\bottomrule
\end{tabular}
\label{table:Recall}
\end{table*}
